QPLIB: A Library of Quadratic Programming Instances

### 2017-01-27 QPLIB-1.0.tex
solvers have merged into solution methods subsection, no need for extra citation

The structure of this paper is the following. In \S~\ref{sec:QPbasic} we review the basic notions about QP. In particular, \S~\ref{subsec:notation} sets out the notation, \S~\ref{sec:classification} proposes a---to the best of our knowledge, new---taxonomy of QP that helps us in discussing the (very) different classes of QPs, \S~\ref{sec:algo} very briefly reviews the solution methods for QP upon which the solvers we have employed are based, and \S~\ref{subsec:solver} describes the solvers.
Then, \S~\ref{sec:lib} describes the process used to obtain the library and its results.
%; the software tools that we have used, and that are freely released together with the library, are discussed in \S~\ref{subsec:tools}. 
Some conclusions are drawn in \S~\ref{sec:conclusions}, after which Appendix A provides a complete description of all the instances of the library, while Appendix B describes the QPLIB file format.

>>>>

The structure of this paper is the following. In \S~\ref{sec:QPbasic} we review the basic notions about QP. In particular, \S~\ref{subsec:notation} sets out the notation, \S~\ref{sec:classification} proposes a---to the best of our knowledge, new---taxonomy of QP that helps us in discussing the (very) different classes of QPs, \S~\ref{sec:algo} very briefly reviews the solution methods for QP and the solvers we have employed.
Then, \S~\ref{sec:lib} describes the process used to obtain the library and its results.
%; the software tools that we have used, and that are freely released together with the library, are discussed in \S~\ref{subsec:tools}. 
Some conclusions are drawn in \S~\ref{sec:conclusions}, after which Appendix A provides a complete description of all the instances of the library, while Appendix B describes the QPLIB file format.
